Andres Karjus

### 2021-04-21 index.Rmd
news

- Hosted a student via the job shadowing (töövari) programme of the Estonian Tagasi Kooli programme (November 2020).
- I helped my supervisor Prof. Kenny Smith carry out a number of linguistics workshops in primary schools around Edinburgh and Lothian, in school years 2018/2019 and 2019/2020.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do other things, which mostly consist of dance (lindy hop, salsa, bachata), jazz, outdoorsy stuff (cycling, hillwalking), boardgames, and various other things.

>>>>

- Hosted students at the CUDAN lab via the job shadowing (töövari) programme of the Estonian Tagasi Kooli programme (online April 2021, live in November 2020).
- I helped my supervisor Prof. Kenny Smith carry out a number of linguistics workshops in primary schools around Edinburgh and Lothian, in school years 2018/2019 and 2019/2020.
- Entered [a video](https://www.youtube.com/watch?v=t8InfFEIINc) to Science Magazine's 11th [Dance Your Ph.D contest](https://www.sciencemag.org/projects/dance-your-phd). The idea is to explain your research topic to the general public though interpretive dance. We didn't win but it was a fun one to do!
- Co-organized the bimonthly [Edinburgh Language Lunch](http://groups.inf.ed.ac.uk/langlunch/) during 2016-2018. 
- Co-organized the [Linguistics and English Language Postgraduate Conference](http://www.lel.ed.ac.uk/~pgc/) of 2017 in Edinburgh, the [Why Linguistics Conference](http://whylinguistics.ut.ee) (2015) and the [Graduate Conference on Areal Linguistics, Grammar and Contacts](http://arealling.ut.ee) (2012) in Tartu, Estonia.

@@

Besides research and teaching and consulting and whatnot, I (fortunately) also do other things, which mostly consist of dance (lindy hop, salsa, bachata), boardgames, and outdoorsy stuff (running, hillwalking).
